InteroceptionStudy_GPValidation

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

@@

install.packages('gazepath')
library(gazepath)
GUI()

@@

# Import Ledalab
Ledalab('/Users/heliocuve/Documents/InteroStudy/EATProcesing/EAT/forLeda/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 105 .01 2])
```{r}
read_leda <- function(flnm) {
  data.table::fread(flnm) %>% 
    mutate(filename = flnm)
}

>>>>

203
270

@@

# install.packages('gazepath')
library(gazepath)
GUI()

@@

# Import Ledalab
Ledalab('/Users/heliocuve/Documents/InteroStudy/EATProcesing/EAT/forLeda/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 105 .01 2])

```{r}
read_leda <- function(flnm) {
  data.table::fread(flnm) %>% 
    mutate(filename = flnm)
}
